\begin{Large}
    Chocolate Snickerdoodles
\end{Large}

\begin{scriptsize}
\begin{multicols}{2}
[
\vspace{1em}
Yields: 1 Unit
\vspace{-1.5em}
]

Dough Ingredients
\begin{itemize}
    \item 0.5 cup butter unsalted, softened
    \item 0.75 cups granulated sugar
    \item 1 large eggs
    \item 0.5 teaspoon pure vanilla extract
    \item 2 ounces unsweetened chocolate melted and cooled
    \item 1.38 cup all-purpose flour
    \item 0.75 teaspoons cream of tartar
    \item 0.13 cup unsweetened cocoa powder
    \item 0.5 teaspoon baking soda
    \item 0.25 teaspoon baking
\end{itemize}

Topping Ingredients
\begin{itemize}
    \item 0.17 cup granulated sugar
    \item 0.75 tablespoons ground cinnamon
\end{itemize}
\end{multicols}
\end{scriptsize}

\begin{footnotesize}
\begin{enumerate}
    \item For the dough:
    \item Add butter and sugar to a bowl of a stand mixer. With a paddle attachment, cream butter and sugar together on medium until smooth, about 3 minutes. Add eggs one at a time. Add vanilla extract and cooled, melted chocolate and mix on low just until mixed.
    \item In a separate bowl, whisk flour, cream of tartar, cocoa powder, baking soda, baking powder, and salt together until combined. While turned off, add 1 cup of flour mixture to the butter mixture. Mix on low until combined. Add in another cup of flour mixture and combine on low. Add in the remaining flour mixture and mix just until combined.
    \item Line a baking sheet with parchment paper. Scoop dough with a small cookie scoop and place on parchment paper. Repeat with all of the dough. Cover the balls of dough with a tight piece of plastic wrap. Chill for at least 2 hours.
    \item Baking the cookies:
    \item Once chilled, remove the dough balls from the refrigerator. Preheat oven to 350 degrees. Prepare two baking sheets by lining with parchment paper.
    \item Add cinnamon and remaining granulated sugar together in a small bowl and mix with a spoon. Roll a ball of chilled dough between your hands until smooth and even. Toss in cinnamon sugar until coated. Place on prepared baking sheet. Repeat with the rest of the balls, setting them about 1 1⁄2 inches apart on baking sheet. You may need a third baking sheet to fit them all. Do not discard remaining cinnamon sugar.
    \item Bake in preheated oven for about 12 minutes or until the cookies begin to crack around the edges. Remove from oven and let them cool for 5 minutes. Very gently, remove a cookie fromthe baking sheet with a fork and place in remaining cinnamon sugar. Flip it to coat the other side. Place back on baking sheet and repeat with the rest. Eat them immediately or store in covered container for up to 3 days.
\end{enumerate}
\end{footnotesize}

\vspace{2em}
