\begin{Large}
    Chocolate Cake
\end{Large}

\begin{scriptsize}
\begin{multicols}{2}
[
\vspace{1em}
Yields: 1 Unit
\vspace{-1.5em}
]

Cake Ingredients
\begin{itemize}
    \item 1 stick butter
    \item 1/2 cup cooking oil (Crisco or Wesson)
    \item 4 Tablespoons cocoa
    \item 1 cup water
    \item 2 cups flour
    \item 1 teaspoon baking soda
    \item 2 cups sugar
    \item 1/2 cup butter milk (OR—place 1 1/2 teaspoons vinegar in 1/2 cup measure, fill with milk)
    \item 2 eggs
    \item 1 teaspoon cinnamon
    \item 1 teaspoon vanilla
\end{itemize}

Frosting Ingredients
\begin{itemize}
    \item 1 stick butter
    \item 4 Tablespoons cocoa
    \item 6 Tablespoons milk
    \item 1 lb box powdered sugar
    \item 1 teaspoon vanilla
    \item 1/2 cup chopped pecans (optional)
\end{itemize}
\end{multicols}
\end{scriptsize}

\begin{footnotesize}
\begin{enumerate}
    \item Combine butter, oil, cocoa, and water in a saucepan and heat until butter is melted---stir well---do not boil.
Set aside. 
    \item Combine flour, baking soda, sugar, sour milk, eggs, cinnamon, and vanilla in large mixing bowl.
    \item Beat until all mixed and blended well.
    \item Pour in chocolate mixture—beat.
    \item Spray 9 X 13 with Bakers Joy (or grease and flour pan).
    \item Pour batter into 9 X 13 pan.
    \item Bake 350 degrees for 30-35 minutes (Bake time depends on pan---start checking at 25 minutes).
    \item Frost while cake is warm.

    \item Combine butter, cocoa, milk in a saucepan and heat until bubbles form around the edge.
    \item Remove from heat.
    \item Add powdered sugar, a little at a time, vanilla and pecans.
    \item Beat well.
\end{enumerate}
\end{footnotesize}

\vspace{2em}
