\begin{Large}
    Deviled Eggs
\end{Large}

\begin{scriptsize}
\begin{multicols}{2}
[
\vspace{1em}
Yields: 24 Units
\vspace{-1.5em}
]

Whites
\begin{itemize}
    \item 1 cup plain yogurt
    \item 1/2 cup unsweetened milk
    \item 3/4 tsp agar agar powder
    \item 1/4 tsp kala namak (black salt)
\end{itemize}

Yolks
\begin{itemize}
    \item 6 tbsp boiled tofu
    \item 1/4 cup mayonnaise
    \item 1/4 cup mustard
    \item 3 tbsp relish
    \item 1/2 tsp kala namak (black salt)
    \item 1/8 tsp cayenne pepper
    \item Salt and pepper to taste
    \item Paprika for garnish
%    \item 2 Tbsp mayonnaise
%    \item 2 Tbsp vegetable oil
%    \item 2 tsp dijon mustard
%    \item 1 tsp white wine vinegar
%    \item 3/4 tsp salt
%    \item 1/2 tsp kala namak (black salt)
%    \item 1/2 tsp turmeric
%    \item Black pepper to taste
%    \item Paprika, for garnish
\end{itemize}
\end{multicols}
\end{scriptsize}

\begin{footnotesize}
\begin{enumerate}
    \item Combine almond milk, agar agar, and kala namak in a small saucepan and whisk to combine. Bring to a boil. Remove
from heat and pour into egg molds. Refrigerate for 30 minutes to allow to set.
\item Combine tofu, vegan mayo, oil, mustard, vinegar, salt, black salt, turmeric and pepper in a food processor or blender.
Blend 30 seconds or until smooth.
\item Use a half-teaspoon or melon baller to scoop out a small circle from the inside of each egg half.
\item Place the yolks in a piping bag fitted with a star tip. Fill each egg with yolk (alternatively, just use a spoon to scoop some
yolk into each egg).
\item Sprinkle with paprika and serve.

\end{enumerate}
\end{footnotesize}

\vspace{2em}
