\begin{Large}
    Roast with Filling
\end{Large}

\begin{scriptsize}
\begin{multicols}{2}
[
\vspace{1em}
Yields: 4 Units
\vspace{-1.5em}
]

Filling
\begin{itemize}
    \item 2 cups fresh mushrooms, chopped
    \item 2 large garlic cloves, minced
    \item 1/2 cup nuts (pecans \&/or walnuts) chopped
    \item 1/2 cup artichoke hearts
    \item 1/2 cup GF Glutino table crackers, crushed (or original water crackers if not GF)
    \item 1/4 teaspoon salt
    \item 1/8 teaspoon red crushed pepper
    \item 1 tablespoon olive oil
\end{itemize}

Roast
\begin{itemize}
    \item 1 pound extra firm tofu
    \item 1/4 cup tapioca starch
    \item 1/4 cup rice flour
    \item 1 tablespoon nutritional yeast
    \item 1/4 teaspoon thyme
    \item 1/2 teaspoon sage
    \item 1 teaspoon garlic powder
    \item 2 teaspoon onion powder
    \item pinch of cayenne (optional)
    \item 2 tablespoon dried mushroom powder (powdered dried mushrooms)
    \item 1 teaspoon agar powder (dissolved in warm Bragg Liquid Aminos)
    \item 2 tablespoon Bragg Liquid Aminos
    \item 2 tablespoon oil (optional)
    \item 1/2 teaspoon salt
    \item 1 teaspoon Better Than Bouillon (or chicken-style seasoning)
\end{itemize}

Glaze
\begin{itemize}
    \item 1 tablespoon oil
    \item 2 teaspoons Bragg Liquid Aminos
    \item 1 tsp maple syrup
\end{itemize}
\end{multicols}
\end{scriptsize}

\begin{footnotesize}

Filling
\begin{enumerate}
    \item In a skillet sauté mushrooms in olive oil for a couple of minutes.
    \item Add minced garlic and sauté for another minute.
    \item Next add the mushroom garlic mixture to a food processor and the remaining ingredients: artichoke hearts, chopped nuts, crackers, salt, and red crushed pepper.
    \item Pulse a few times to combine. Set aside.
\end{enumerate}

Roast
\begin{enumerate}
    \item Preheat oven to 350F
    \item In a food processor add the extra firm tofu. Pulse to blend.
    \item In a small glass jar add the agar powder to the Bragg Liquid Aminos and stir.
    \item Place in microwave for a few seconds to heat.
    \item This is a crucial step.
    \item Add to the food processor.
    \item Next, add all the remaining ingredients.

    \item Blend until it forms a very soft dough.
    \item Transfer dough to parchment paper.
    \item Place another parchment paper on top. 
    \item Flatten by using hands to get the desired rectangle shape. 
    \item Gently remove the top parchment paper.
    \item Add the filling to the middle. 
    \item Gently pull the parchment paper together over the filling. 
    \item Squeeze the two edges of the dough together at the top using the parchment paper. 
    \item Roll the parchment paper from top down until you reach the roast. 
    \item Pull the parchment paper tightly around the roast, forming it into a roll.
    \item Twist the sides. 
    \item Take your time, as this is the shape of the final roast.
    \item Cover with a piece of foil. (Foil is helpful to keep the shape of the roast, but not necessary)

    \item Bake at 350F for 90 minutes, flipping the roast half way through cooking time.
    \item Let roast cool and store in the fridge for several hours before serving. 
    \item This is a crucial step that will set the texture and make it easier to cut and handle.
    \item When ready to serve, heat in the oven at 350F for 20-30 minutes.

    \item Baste with the below glaze, which will make the crust crisp and tasty.
\end{enumerate}

Glaze
\begin{enumerate}
    \item Whisk to combine. 
    \item Brush on with pastry brush before reheating.
    \item Serve with blanched Brussels sprouts, cranberries, potatoes and gravy.

    \item The glaze can also be added in a skillet right before serving.
\end{enumerate}
\end{footnotesize}

\vspace{2em}
